---
name: Diego
surname: Aguilar-Ramirez
position: "Early-Career Research Fellow"
address: "University of Oxford, UK"
phone: +44 738 0447770
email: "diego.aguilar-ramirez@ndph.ox.ac.uk"
github: "diegojehu"
site: ctsu.ox.ac.uk/team/diego-aguilar-ramirez
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Medic, clinical epidemiologist, and population health scientist with a strong interest in cardiometabolic diseases in the Mexican population."
output: 
  vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Employment
```{r employment}
jobs <- do.call("bind_rows",
  rorcid::orcid_employments("0000-0003-2298-3768")$`0000-0003-2298-3768`$`affiliation-group`$summaries
)

jobs %>%
  mutate(`employment-summary.end-date.year.value` = replace(`employment-summary.end-date.year.value`, is.na(`employment-summary.end-date.year.value`), "Present")) %>%
  detailed_entries(
    with = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}"),
    what = `employment-summary.organization.name`,
    where = `employment-summary.organization.address.city`
  )
```

# Education
```{r education}
edu <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0003-2298-3768")$`0000-0003-2298-3768`$`affiliation-group`$summaries
)

edu %>%
  mutate(`education-summary.end-date.year.value` = replace(`education-summary.end-date.year.value`, is.na(`education-summary.end-date.year.value`), "Present")) %>%
  detailed_entries(
    with = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    what = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
```

# Scholarships & Awards
```{r awards}
library(tibble)
tribble(
  ~ Title, ~ Institution, ~ Year, ~ Where,
  "Early-Career Research Fellowship", "Nuffield Department of Population Health", "2022", "Oxford, UK",
  "BHF CRE Graduate Studentship - Cardiovascular Population Health Sciences", "Oxford British Heart Foundation Centre for Research Excellence", "2018", "Oxford, UK",
  "Departmental Scholarship - DPhil Population Health", "Nuffield Department of Population Health", "2018", "Oxford, UK",
  "Departmental Scholarship - MSc Global Health Science", "Nuffield Department of Population Health", "2017", "Oxford, UK",
  "Community Service in Medicine Award", "Universidad Panamericana, School of Medicine", "2015", "Mexico City, MX",
  "CENEVAL Award for Excellent Performance in Medical School", "National Centre for the Evaluation of Higher Education", "2015", "Mexico City, MX",
  "Scholarship", "Universidad Panamericana, School of Medicine", "2009", "Mexico City, MX",
) %>% 
  detailed_entries(
    with = Title,
    when = Year,
    what = Institution,
    where = Where)
```

# Publications
```{r publications}
scholar::get_publications("J8t2FMAAAAAJ") %>%
  arrange(., desc(year)) %>%
  filter(year > 2017, !journal %in% c("medRxiv")) %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

# Data Analysis Skills & Experience
```{r data_skills}
tribble(
 ~Year, ~Title, ~Desc,
 2022, "Unix Shell", "Within the high-performance Biomedical Research Computing (BMRC) system",
 2022, "Git", "Version control with local and remote repositories",
 2022, "Python", "Workflow development for genome-wide bioinformatics analyses",
 2020, "RMarkdown", "Development of reproducible reports",
 2018, "R", "Data analysis, statistical modelling, and visualization",
 2018, "SAS", "Data analysis, statistical modelling, and visualization",
 2017, "STATA", "Data analysis and visualization"
) %>%
 brief_entries(
   Desc,
   Title,
   Year
 )
```

# Research Student Supervision
* Currently involved in direct supervision of 2 post-graduate students (1 MSc & 1 DPhil)

# Teaching Experience & Training
* **Teaching assistant** - MSc in Global Health Science and Epidemiology **(2019 - Present)**  
* **Lecturer** - Practical Statistics for Epidemiology Using R **(2021 - Present)**  
* Preparing for Learning and Teaching at Oxford (**2019**)  

# Mentoring
Mentor at the UNIQ+ Digital Program - University of Oxford  (**2020 - Present**)
```{r}
#tribble(
#  ~Year, ~Title, ~Desc,
#  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
#  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
#) %>% 
#  brief_entries(
#    glue::glue("Nobel Prize in {Title}"),
#    Year, 
#    Desc
#  )
```


```{r}
#library(dplyr)
#knitr::write_bib(c("vitae", "tibble"), "packages.bib")

#bibliography_entries("packages.bib") %>%
 # arrange(desc(author$family), issued)
```

